LC-MS ^13^C Lactate Measurements

### 2022-12-21 analysis/glc6-lactate.qmd
edit glc6 lactate report

@@

fluxes |> 
  filter(experiment == "substrate")
df_drift |> 
  filter(type %in% letters[1:3]) |> 
  filter(metabolite == "LAC M0") |> 
  left_join(pheno, by = "number") |> 
  group_by(type, oxygen, time) |> 
  wmo::remove_nested_outliers(area, remove = TRUE) |> 
  summarize(area = mean(area)) |> 
  ggplot() +
  aes(
    x = time, 
    y = area, 
    color = oxygen
  ) +
  geom_point() +
  stat_summary(
    geom = "line"
  )
```

These plots suggest that, for the 100 μL extraction buffer, the maximum cell count is ~ 250,000. We will exclude the 300,000 value prior to calculating the slopes of the curves. For the PASMC samples, the 400,000 cell sample is quite high compared to the other samples. I will also remove these values prior to calculation of the slopes.

>>>>

Lactate peak areas were normalized to the internal standard peak area to generate a standard curve. Sample concentrations were interpolated after correcting the M3 peak areas for quadrupole bias prior to flux calculations.

@@

fluxes |> 
  filter(experiment == "substrate") |> 
  ggplot() +
  aes(
    x = oxygen, 
    y = flux, 
    fill = oxygen
  ) +
   stat_summary(
    geom = "col", 
    fun = "mean", 
    show.legend = FALSE
  ) +
  geom_point(
    color = "white", 
    pch = 21, 
    show.legend = FALSE
  ) + 
  stat_summary(
    geom = "errorbar", 
    width = 0.2, 
    fun.data = "mean_se", 
    linewidth = 0.25
  ) +
  labs(
    x = "Oxygen", 
    y = "Flux (fmol/cell/h)"
  )
```

These data are consistent with the results obtained from enzymatic measurements of extracellular lactate demonstrating decreased lactate efflux from glycolysis in hypoxia compared to normoxia.
